Analysis PPM-S

### 2020-04-06 production/prod_analysis-cfa.rmd
update durante reunion

---
title: "Analysis"
date: "`r format(Sys.time(), '%d %B, %Y')`"
css: "../input/bib/style.css"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_float: true
    toc_depth: 2
    code_folding: "hide"
editor_options: 
  chunk_output_type: console
---

# Analysis PPM-S

This section, documents all the procedures related to the data analysis and measurement models.

@@

@@

4. **Version 04:** Complete sample (N=`r dim(dat04)[1]`)

@@

## Version 04 (N=`r dim(dat04)[1]`)

>>>>

---
title: "Analysis PPM-S"
date: "`r format(Sys.time(), '%d %B, %Y')`"
css: "../input/bib/style.css"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_float: true
    toc_depth: 2
    code_folding: "hide"
editor_options: 
  chunk_output_type: console
---

This section, documents all the procedures related to the data analysis and measurement models.
(description)

@@

Design: this wave ....

@@

4. **Complete Sample:** Complete sample (N=`r dim(dat04)[1]`)

@@

## Complete sample (N=`r dim(dat04)[1]`)
